---
title: "Final Project"
author: "Michael Bevilacqua, Jonah Kotzen, Jaan Selod"
date: "2024-04-23"
output: html_document
bibliography: BIOL5380.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(av)
```

# Introduction:


The  Myctophidae family includes the species *Diaphus mollis*, mesopelagic fish that reach body lengths of 6.6 cm [@Froese2024]. These myctopids are often called lantern fish, and can be found in Atlantic and Indian Oceans. have a high evolutionary radiation, with high variability in phenotypes. This has resulted in the Myctophidae being one of the most abundant and "most species-rich deep-sea fish groups" @Tuset2018there. In this study, we will be looking at the effect of K치rm치n vortices on several deceased Diaphus mollis, which vary in size. These vortices form after a constant flow of water hits an object in the water, which in a natural habitat could be a rock, or a tree, however in this circumstance, a wooden dowel is used. When the myctophid is placed in this street of vortices, fish "swimming behind cylinders adopt a distinctive, previously undescribed pattern of movement in order to hold station, which we term the K치rm치n gait" @Liao2003there. This study will look to analyze ...

picture?

metadata: specimen_speed.csv

# Methods:

- dead myctophids and water tunnel
- iPhone video recording software --> ImageJ with MTrackJ plugin --> coordinates

# Results:
```{r loadinfo, echo = F, warning = F, message = F}
specimens <- read.csv("specimen_info.csv")
specimens %>%
  kable(caption = "Table 1: Specimen Information")
```

```{r vidanalysis, eval = F}
#code used to generate avi files from iphone videos

f <- list.files(full.names = T, pattern = ".MOV")
dir.create("images")
for (i in f) {
  if(dir.exists("images")) unlink("images", recursive = T)
  av_video_images(i, destdir = "images", format = "tiff")
  f.i <- list.files("images", full.names = T)
  av_encode_video(f.i, gsub("MOV", "avi", basename(i)), codec = "rawvideo")
}
```


# Discussion:

# Author Contributions:

# References:
